Forecasting the 2024 US Presidential Election

### 2024-10-17 paper/paper.qmd
Added Data description

@@

*Person A:* Discuss the survey design, the process of data collection, and potential biases or errors in measurement.

@@

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

*Person A:*: Visualize variable distributions (e.g., histograms, boxplots), and justify the inclusion of predictors in the model.

@@

*Person B*: Discuss limitations of the model and areas for further improvement.

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

Our objective was to clean, organize, and analyze polling data for the U.S. presidential general election. Below is an outline of the steps we took to achieve this goal:

### 1. **Cleaning Raw Poll Data**
We began by identifying the three most frequent pollsters within the dataset, focusing on these pollsters to improve data reliability and relevance. Missing values were assessed for each pollster, and the pollster with the fewest missing values was selected to ensure more complete data for further analysis. This refined dataset was then saved for the next stages of the process.

### 2. **Organizing Poll Links by State**
Next, we organized the polling data by state, ranking the links for each state to facilitate easier access. To ensure clarity, missing values were shifted to the end of each state’s record, and unnecessary empty columns were removed. This resulted in a more structured and user-friendly dataset, which was stored for future use.

### 3. **Extracting and Merging Poll Data from Links**
Following that, we extracted and merged additional polling data from Google Sheets links included in the dataset. After confirming the validity of these links, we cleaned the data by removing unwanted entries and filled in any missing values where possible. This updated dataset was then merged with the original dataset to create a more comprehensive compilation of polling data.

### 4. **Final Organization and Refinement**
In the final stage, we further refined the dataset by removing unnecessary rows (such as totals and empty states) and renaming specific entries for clarity (e.g., changing "State" to "National"). Columns with excessive missing values were also eliminated to ensure that only the most reliable and complete data remained. This final, polished dataset was saved, ready for subsequent analysis and reporting.

@@

*Person C:* Discuss the survey design, the process of data collection, and potential biases or errors in measurement.

@@

@@

*Person B:*: Visualize variable distributions (e.g., histograms, boxplots), and justify the inclusion of predictors in the model.

@@

*Person C*: Discuss limitations of the model and areas for further improvement.

@@

@@
